---
title: "Save forLater"
output: html_document
---

---
title: "Chapter 2 Carrizo"
output: html_document
---
###Load Data
```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(meta)
library(PRISMAstatement)
library(skimr)
library(MASS)
library(ggpubr)
setwd("/R Packages/Chapter 2")
```

```{r, message=FALSE, warning=TRUE}
###Load all necessary .csv files
setwd("/R Packages/Chapter 2")
photo <- read_csv("Carrizo Shrub Photo density Sheet.csv")
colnames(photo)[6] = "site"
photo$site <- as.character(photo$site)
focal <- read_csv("Focal Observations Data Sheet.csv")
focal$Site <- as.character(focal$Site)
transect <- read_csv("Transect Data Sheet.csv")
transect$Site.Number <- as.character(transect$Site.Number)
cam.location <- read_csv("Camera Location data Sheet.csv")
str(transect)

shrub <- read.csv("Site Data Sheet.csv")
```


### Data Set-up
```{r}
###Give Summary of photo data
summary(photo)
```

```{r}
count.hit <- photo %>%
  count(animal.hit) %>%
  na.omit()
summary(count.hit)

###Camera recorded an animal 2.705% of the time. Not too bad
```
```{r}
skim(photo)
```
```{r}
###Transect Data

summary(transect)
```

```{r}
tran.hit <- transect %>%
  count(animal.hit) %>%
  na.omit()
summary(tran.hit)
```

```{r}
skim(transect)
```
```{r}
tran.hit %>%
  ggplot(aes(animal.hit, n)) + geom_col() + theme_classic() + xlab("Hits") + ylab("Count") + ggtitle("Hits during Transects")
```
```{r}
####Summary capture data on Transects
transect.data <- transect %>%
  group_by(Site, Site.Number, Site.Density) %>%
  summarise(captures = sum(animal.hit), n = n(), animal.richness = n_distinct(RTM)-1) %>% mutate(rate = captures/n) #-1 for richness bc of none as level
transect.data$rate <- as.character(transect.data$rate)

###Summary Transect Animal Data
transect.diversity <- transect %>%
  group_by(Site, Site.Number, Site.Density) %>%
  summarise(captures = sum(animal.hit), n = n()) %>% mutate(rate = captures/n)

unique(transect.diversity$Site.Density)
```
```{r}
transect.level <- transect %>%
  group_by(Site, Site.Number, Site.Density, Date) %>%
  summarise(captures = sum(animal.hit), n = n()) %>% mutate(rate = captures/n)

unique(transect.level$Site.Density)
```

```{r}
###Data Viz for number of hits during photo analysis
count.hit %>%
  ggplot(aes(animal.hit, n)) + geom_col() + theme_classic() + xlab("Hits") + ylab("Count") + ggtitle("Number of total animal hits")
```
```{r}
###Summary Capture Data
data <- photo %>%
  group_by(region, site, week, `level (l,m,h,none)`, rep, camera.number) %>%
  summarise(captures = sum(animal.hit), n = n(), animal.richness = n_distinct(RTU)-1) %>% mutate(rate = captures/n) #-1 for richness bc of none as level
data$rep <- as.character(data$rep)

###Summary Animal Data
diversity <- photo %>%
  group_by(region, site, `level (l,m,h,none)`, RTU) %>%
  summarise(captures = sum(animal.hit), n = n()) %>% mutate(rate = captures/n)

unique(diversity$RTU)
```

```{r}
###Summary level Data
level <- photo %>%
  group_by(region, site, week, rep, `level (l,m,h,none)`) %>%
  summarise(captures = sum(animal.hit), n = n()) %>% mutate(rate = captures/n)

unique(level$`level (l,m,h,none)`)
```

```{r}
animals <- photo %>%
  group_by(region, site, RTU) %>%
  summarise(captures = sum(animal.hit), n = n()) %>% mutate(rate = captures/n)

unique(animals$RTU)
```

```{r}
summary(shrub)
```

```{r}
###Data for shrub size and total number of shrubs in each site. (Ask Chris about)
shrub.size <- shrub%>%
  group_by(site.number, site.density, shrub.count, x, y, z) %>%
  summarise(volume = sum(x*y*z))
```

```{r}
##Clean up focal data
focal.data <- focal %>%
  count(animal.hit) %>%
  na.omit()

skim(focal)
focal.data <- focal %>%
  group_by(Site, site.density) %>%
  summarise(captures = sum(animal.hit), n = n(), animal.richness = n_distinct(RTU)-1) %>% mutate(rate = captures/n)

unique(transect.level$Site.Density)

focal.site <- focal%>%
  group_by(Site, site.density, Date) %>%
  summarise(captures = sum(animal.hit), n = n(), animal.richness = n_distinct(RTU)-1) %>% mutate(rate = captures/n)
```


###Data Viz
```{r}
###Total captures between site levels

ggplot(level, aes(`level (l,m,h,none)`, captures)) +
  geom_boxplot() + 
  labs(y = "total captures", x = "site density") + ggtitle("Number of Total Animal Hits in Camera Traps")
```
```{r}
###Capture rate per site level
ggplot(level, aes(`level (l,m,h,none)`, rate)) +
  geom_boxplot() + 
  labs(y = "capture rate", x = "site density")
```


```{r}
ggplot(transect.level, aes(rate, captures, color = Site.Density)) +
         geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "Rate of Capture", y = "total captures")
```
```{r}
require(mgcv)
ggplot(transect.level, aes(rate, captures, color = Site.Density)) +
         stat_smooth(method = "gam") +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "Rate of Capture", y = "total captures")
```

```{r}
ggplot(transect.level, aes(n, captures, color = Site.Density)) +
         geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "n", y = "total captures")
```
```{r}
require(mgcv)
ggplot(transect.level, aes(n, captures, color = Site.Density)) +
         stat_smooth(method = "gam") +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "n", y = "total captures")
```

```{r}
ggplot(transect.level, aes(rate, n, color = Site.Density)) +
         geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "Rate of Capture", y = "n")
```
```{r}
require(mgcv)
ggplot(transect.level, aes(n, rate, color = Site.Density)) +
         stat_smooth(method = "gam") +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~Site.Density, scales = "free") +
  labs(color = "", x = "n", y = "rate")
```

```{r}
###Diversity Plot from Photo Data looking at Total Captures
excludes <- c("none", "None", "unidentifiable", "unkown", "", "Unidentifiable", "Human")

plot.diversity <- diversity%>%
  filter(!RTU %in% excludes)

ggplot(plot.diversity, aes(RTU, captures, fill = site)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(fill = "", x = "total captures")
```
```{r}
###Diversity Plot from Photo Data looking at Rate
ggplot(plot.diversity, aes(RTU, rate, fill = site)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(fill = "", x = "total captures")
```
```{r}
ggplot(focal.data, aes(n, captures, color = site.density)) +
         stat_smooth(method = "gam") +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~site.density, scales = "free") +
  labs(color = "", x = "captures", y = "rate")
```
Camera Presence Boxplot
```{r}
photopresence <- ggplot(level, aes(`level (l,m,h,none)`, captures, fill = as.character(site))) +
  geom_boxplot() +
  labs(y = "Presence", x = "site density") + theme_classic() + guides(fill=FALSE)
photopresence
```
```{r}
transectpresence <- ggplot(transect.level, aes(Site.Density, captures, fill = as.character(Site.Number))) +
  geom_boxplot() +
  labs(y = "Presence", x = "site density") + theme_classic() + guides(fill=FALSE)
transectpresence
```



Camera Abundance Boxplot
```{r}
ggplot(level, aes(`level (l,m,h,none)`, rate, fill = as.character(site))) +
  geom_boxplot() +
  labs(y = "Abundance", x = "site density")
```


Focal Presence Boxplot
```{r}
focalpresence <- ggplot(focal.site, aes(site.density, captures, fill = as.character(Site))) +
  geom_boxplot() + guides(fill=FALSE) + theme_classic() + xlab("site density") + ylab("Presence")

focalpresence
```

###Focal abundance Boxplot
```{r}
ggplot(focal.site, aes(site.density, rate, fill = as.character(Site))) +
  geom_boxplot() +
  labs(y = "abundance", x = "site density")
```


##Stats
###Stats for capture compare to level
```{r}
m <- glm(captures~`level (l,m,h,none)`, data = level) #capture difference between microsite
summary(m)
```
```{r}
### Test if data is significant
anova(m, test = "Chisq")

####ITS SIGNIFICANT!!!
```
```{r}
shapiro.test(m$residuals)

###Data is not Normally distributed
```
```{r}
library(lsmeans)
lsmeans(m, pairwise~`level (l,m,h,none)`, adjust = "Tukey")
```
```{r}
m <- glm(captures~`level (l,m,h,none)`, data = level, family = "quasipoisson")
anova(m)
summary(m)
```


###Stats for Captures by Site
```{r}
m <- glm(captures~site, data = level) #capture difference between microsite
summary(m)
```
```{r}
anova(m, test = "Chisq")
```
```{r}
ggplot(level, aes(`level (l,m,h,none)`, captures, fill = as.character(site))) +
  geom_boxplot() +
  labs(y = "capture rate", x = "site density")
```

```{r}
m <- glm(rate~site, data = level) #capture difference between microsite
summary(m)
```
```{r}
m <- glm(rate~`level (l,m,h,none)`, data = level) #rate of capture between microsites
summary(m)
```
```{r}
anova(m, test = "Chisq")
```


```{r}
ggplot(level, aes(`level (l,m,h,none)`, rate)) +
  geom_boxplot() +
  labs(y = "capture rate", x = "site density")
```


###Stats for rate of capture between Levels
```{r}
mp <- glm(rate~`level (l,m,h,none)`, data = level, family = "quasipoisson")
summary(mp)
```
```{r}
anova(mp, test = "Chisq")
```
```{r}
shapiro.test(mp$residuals)

###Data is not Normally distributed
```
```{r}
library(lsmeans)
lsmeans(mp, pairwise~`level (l,m,h,none)`, adjust = "Tukey")
```

###Stats for Transect captures
```{r}
###Boxplot for Transect Captures
ggplot(transect.data,  aes(Site.Density, captures)) +
  geom_boxplot() +
  labs(y = "capture", x = "site density")
```

```{r}
mt <- glm(captures~Site.Density, data = transect.level, family = "poisson")
summary(mt)
```
```{r}
anova(mt, test = "Chisq") #get p-value for model
```
```{r}
shapiro.test(mt$residuals) #explore residuals
```
```{r}
library(emmeans)
library(lsmeans)
lsmeans(mt, pairwise~Site.Density, adjust = "Tukey")
```
```{r}
mt <- lm(captures~Site.Number, data = transect.level)
summary(mt)
```


```{r}
mt <- glm(rate~Site.Density, data = transect.level)
summary(mt)
```
```{r}
anova(mt, test = "Chisq")
```
###Look at Stats for varying density level by individual sites for cameras
```{r}
library(emmeans)
mg <- glm(captures~`level (l,m,h,none)`*as.factor(site), family = "quasipoisson", data = level)
summary(mg)
anova(mg, test = "Chisq")
emmeans(mg, pairwise~`level (l,m,h,none)`)
```
regression curve needed!!!!!

###Look at Stats for varying density level by individual sites for Transects
```{r}
library(emmeans)
mt <- glm(captures~Site.Density*as.factor(Site.Number), family = "quasipoisson", data = transect.level)
summary(mt)
anova(mt, test = "Chisq")
emmeans(mt, pairwise~Site.Density)
```
###Look at the rate of capture difference between the sites (Cameras)
```{r}
mg <- glm(rate~`level (l,m,h,none)`*as.factor(site), family = "quasipoisson", data = level)
summary(mg)
anova(mg, test = "Chisq")
emmeans(mg, pairwise~`level (l,m,h,none)`)
```
###Looks at the rate of capture between site densities (Transects)
```{r}
mt <- glm(rate~Site.Density*as.factor(Site.Number), family = "quasipoisson", data = transect.level)
summary(mt)
anova(mt, test = "Chisq")
emmeans(mt, pairwise~Site.Density*as.factor(Site.Number))
```


```{r}
mod <- lm(captures~`level (l,m,h,none)`*as.factor(site), data = level)
summary(mod)
```



```{r}
ggplot(level, aes(rate, captures, color = `level (l,m,h,none)`)) +
         geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~`level (l,m,h,none)`, scales = "free") +
  labs(color = "", x = "Rate of Capture", y = "captures")
```
##Captures for Photo Data Stats
```{r}
library(emmeans)
mg <- glm(captures~`level (l,m,h,none)`*as.factor(site) + offset(log(n)), family = "quasipoisson", data = level)
anova(mg, test = "Chisq")
emmeans(mg, pairwise~`level (l,m,h,none)`*as.factor(site))
```



###Interpretation
1) 
##Things still to do
1) Figure out how to do abundance for images
2) Figure out how to do diversity for images
3) Build a species list off what we founf in camera traps



###Diversity Data for Photos
```{r}
library(tidyverse)
library(vegan)
photovegan <- photo %>%
  group_by(region, site, rep, `level (l,m,h,none)`, RTU) %>%
  summarise(captures = sum(animal.hit))

photovegan$region <- gsub(" ", "", photovegan$region)
photovegan$region <- as.factor(photovegan$region)
photovegan$uniID <- paste(photovegan$site, photovegan$`level (l,m,h,none)`)
str(photovegan)
```

```{r}
library(dplyr)
photovegan <- photovegan %>% 
  ungroup()%>%
  dplyr::select(uniID, RTU, captures)
photovegan <- photovegan %>% group_by(uniID, RTU) %>% summarise(captures = sum(captures))

comm <- photovegan %>% spread(RTU, captures) %>% dplyr::select(-none, -None)
comm[is.na(comm)] <- 0
```

```{r}
comm <- comm %>%
  ungroup() %>%
  dplyr::select(-uniID)
```

```{r}
siteshort <- read_csv("site desntiy shortcut.csv")

shortvegan <- siteshort %>%
  group_by(Site, site.density, shrub.count)

shortvegan$shrub.count <- gsub(" ", "", shortvegan$shrub.count)
shortvegan$shrub.count <- as.factor(shortvegan$shrub.count)
shortvegan$uniID <- paste(shortvegan$site.density, shortvegan$site.count)
str(shortvegan)

shortvegan <- shortvegan %>%
  ungroup() %>%
  dplyr::select(uniID, site.density, shrub.count)
shortvegan <- shortvegan %>% group_by(uniID, site.density)

shortvegan <- shortvegan %>%
  ungroup() %>%
  dplyr::select(-uniID)

```

```{r}
Hphoto <- diversity(comm)
simpphoto <- diversity(comm, index = "simpson")
Sphoto <- specnumber(comm)
Jphoto <- Hphoto/log(Sphoto)
shortvegan$H <- Hphoto
shortvegan$Simpson <- simpphoto
shortvegan$Species <- Sphoto
shortvegan$Even <- Jphoto
```

```{r}
ggplot(shortvegan, aes(site.density, Species)) + geom_boxplot() + ylab("Species Diversity (Photo)") + xlab("Site Density") + theme_classic()
ggplot(shortvegan, aes(site.density, Even)) + geom_boxplot() + ylab("Species Evenness (Photo)") + xlab("Site Density") + theme_classic()
plot1 <- ggplot(shortvegan, aes(site.density, H)) + geom_boxplot() + ylab("Species Diversity") + xlab("Site Density") + theme_classic() + ggtitle("Photo")
plot1
```
```{r}
dataphoto <- glm(H~site.density, data = shortvegan)
summary(dataphoto)
```
###Stats to show photo captures
```{r}
anova(dataphoto, test = "Chisq")
emmeans(dataphoto, pairwise~site.density)
```

###Diversity Data for Transects
```{r}
library(tidyverse)
library(vegan)
transectvegan <- transect %>%
  group_by(Site, Site.Number, Site.Density, RTM) %>%
  summarise(captures = sum(animal.hit))

transectvegan$Site.Number <- gsub(" ", "", transectvegan$Site.Number)
transectvegan$Site.Number <- as.factor(transectvegan$Site.Number)
transectvegan$uniID <- paste(transectvegan$Site, transectvegan$Site.Density, transectvegan$Site.Number)
str(transectvegan)
```
```{r}
library(dplyr)
transectvegan <- transectvegan %>% 
  ungroup()%>%
  dplyr::select(uniID, RTM, captures)
transectvegan <- transectvegan %>% group_by(uniID, RTM) %>% summarise(captures = sum(captures))

transectdata <- transectvegan %>% spread(RTM, captures) %>% dplyr::select(-none)
transectdata[is.na(transectdata)] <- 0
transectdata <- transectdata %>%
  ungroup() %>%
  dplyr::select(-uniID)
```

Now put the site data with the transect data (Seperate from the photo data)
```{r}
shorttransect <- siteshort %>%
  group_by(Site, site.density, shrub.count)

shorttransect$shrub.count <- gsub(" ", "", shorttransect$shrub.count)
shorttransect$shrub.count <- as.factor(shorttransect$shrub.count)
shorttransect$uniID <- paste(shorttransect$site.density, shorttransect$site.count)
str(shorttransect)

shorttransect <- shorttransect %>%
  ungroup() %>%
  dplyr::select(uniID, site.density, shrub.count)
shorttransect <- shorttransect %>% group_by(uniID, site.density)

shorttransect <- shorttransect %>%
  ungroup() %>%
  dplyr::select(-uniID)
```
```{r}
Htransect <- diversity(transectdata)
simptransect <- diversity(transectdata, index = "simpson")
Stransect <- specnumber(transectdata)
Jtransect <- Htransect/log(Stransect)
shorttransect$H <- Htransect
shorttransect$Simpson <- simptransect
shorttransect$Species <- Stransect
shorttransect$Even <- Jtransect
```
Figures for transect diversity
```{r}
ggplot(shorttransect, aes(site.density, Species)) + geom_boxplot() + ylab("Number of Species (Transect)") + xlab("Site Density") + theme_classic()
ggplot(shorttransect, aes(site.density, Even)) + geom_boxplot() + ylab("Species Evenness (Transect)") + xlab("Site Density") + theme_classic()
plot2 <- ggplot(shorttransect, aes(site.density, H)) + geom_boxplot() + xlab("Site Density") + theme_classic() + ggtitle("Transect") + ylab("")
```
```{r}
datatransect <- glm(H~site.density, data = shorttransect)
summary(datatransect)
```
```{r}
anova(datatransect, test = "Chisq")
emmeans(datatransect, pairwise~site.density)
```
###Diversity Data for Focal Observations
```{r}
library(tidyverse)
library(vegan)
focalvegan <- focal %>%
  group_by(Site, site.density, RTU) %>%
  summarise(captures = sum(animal.hit))

focalvegan$Site <- gsub(" ", "", focalvegan$Site)
focalvegan$Site <- as.factor(focalvegan$Site)
focalvegan$uniID <- paste(focalvegan$Site, focalvegan$site.density)
str(focalvegan)
```
```{r}
library(dplyr)
focalvegan <- focalvegan %>% 
  ungroup()%>%
  dplyr::select(uniID, RTU, captures)
focalvegan <- focalvegan %>% group_by(uniID, RTU) %>% summarise(captures = sum(captures))

focaldata <- focalvegan %>% spread(RTU, captures) %>% dplyr::select(-none)
focaldata[is.na(focaldata)] <- 0
focaldata <- focaldata %>%
  ungroup() %>%
  dplyr::select(-uniID)
```

```{r}
shortfocal <- siteshort %>%
  group_by(Site, site.density, shrub.count)

shortfocal$shrub.count <- gsub(" ", "", shortfocal$shrub.count)
shortfocal$shrub.count <- as.factor(shortfocal$shrub.count)
shortfocal$uniID <- paste(shortfocal$site.density, shortfocal$site.count)
str(shortfocal)

shortfocal <- shortfocal %>%
  ungroup() %>%
  dplyr::select(uniID, site.density, shrub.count)
shortfocal <- shortfocal %>% group_by(uniID, site.density)

shortfocal <- shortfocal %>%
  ungroup() %>%
  dplyr::select(-uniID)
```



```{r}
Hfocal <- diversity(focaldata)
simpfocal <- diversity(focaldata, index = "simpson")
Sfocal <- specnumber(focaldata)
Jfocal <- Hfocal/log(Sfocal)
shortfocal$H <- Hfocal
shortfocal$Simpson <- simpfocal
shortfocal$Species <- Sfocal
shortfocal$Even <- Jfocal
```

```{r}
ggplot(shortfocal, aes(site.density, Species)) + geom_boxplot() + ylab("Number of Species") + xlab("Site Density") + theme_classic()
ggplot(shortfocal, aes(site.density, Even)) + geom_boxplot() + ylab("Species Evenness") + xlab("Site Density") + theme_classic()
plot3 <- ggplot(shortfocal, aes(site.density, H)) + geom_boxplot() + xlab("Site Density") + theme_classic() + ggtitle("Focal") +ylab("")
```
```{r}
datafocal <- glm(H~site.density, data = shortfocal)
summary(shortfocal)
```
```{r}
anova(datafocal, test = "Chisq")
emmeans(datafocal, pairwise~site.density)
```

So what has been done so far.
1) First couple hundred lines of code display that there is a difference in the number of visitation between site densities. It seems more animals are in the low density area than the Medium, High and None areas
2) I ran the code for diversity for the focal data first and it seems to be significant with high density (seen in GLM) but after running annova and emmeans it says it is not significant
3) I ran the code for diversity of transects and focal observations. Both of which say that there is no significant difference between the Diversity of the sites

```{r}
dataphoto1 <- glm(Even~site.density, data = shortvegan)
anova(dataphoto1, test = "Chisq")
emmeans(dataphoto1, pairwise~site.density)
```
```{r}
ggarrange(plot1, plot2, plot3, nrow = 1, ncol = 3)
```

```{r}
datatransect1 <- glm(Even~site.density, data = shorttransect)
anova(datatransect1, test = "Chisq")
emmeans(datatransect1, pairwise~site.density)
```

```{r}
ggarrange(photopresence, transectpresence, focalpresence, nrow = 2, ncol = 2)
```


```{r}
fig1 <- ggplot(level, aes(`level (l,m,h,none)`, captures)) +
  geom_boxplot() +
  labs(y = "Animal Abundance", x = "Site Density") + theme_classic()
fig2 <- ggplot(transect.data, aes(Site.Density, captures)) +
  geom_boxplot() +
  labs(y = "Animal Abundance", x = "Site Density") + theme_classic()
fig3 <- ggplot(focal.data, aes(site.density, captures)) +
  geom_boxplot() +
  labs(y = "Animal Abundance", x = "Site Density") + theme_classic()
```

```{r}
ggarrange(fig1, fig2, fig3, nrow = 2, ncol = 2)
```

##Set up data to have Photo, Transect and Focals all together with shrub covers!

```{r}
masterphoto <- photo %>%
  group_by(site, plot,  `level (l,m,h,none)`, density_level,Measure, date, day_sample, RTU, microsite) %>%
  summarise(daily_animal_totals = sum(animal.hit))


masterphoto$uniID <- paste(masterphoto$site, masterphoto$`level (l,m,h,none)`)
str(masterphoto)

masterphoto$uniID <- NULL
names(masterphoto)[3] <- "density_category"
```
```{r}
mastertransect <- transect %>%
  group_by(Site.Number, plot, Site.Density, density_level, Measure, Date, day_sample, RTM, microsite) %>%
  summarise(daily_animal_totals = sum(animal.hit))


mastertransect$uniID <- paste(mastertransect$site, mastertransect$Site.Density)
str(mastertransect)
mastertransect$uniID <- NULL
names(mastertransect)[1] <- "site"
names(mastertransect)[3] <- "density_category"
names(mastertransect)[6] <- "date"
names(mastertransect)[8] <- "RTU"
```
```{r}
masterfocal <- focal %>%
  group_by(Site, plot, site.density, density_level, Measure, Date, day_sample, RTU, microsite) %>%
  summarise(daily_animal_totals = sum(animal.hit))


masterfocal$uniID <- paste(masterfocal$Site, masterfocal$site.density)
str(masterfocal)
masterfocal$uniID <- NULL
names(masterfocal)[6] <- "date"
names(masterfocal)[1] <- "site"
names(masterfocal)[3] <- "density_category"

```
```{r}
masterphotofocal <- merge(masterphoto, masterfocal, all=TRUE)

masterdata <- merge(masterphotofocal, mastertransect, all=TRUE)
names(masterdata)[8] <- "species"
names(masterdata)[5] <- "method"
names(masterdata)[7] <- "sample_day"

write.csv(masterdata, "data_2019_compiled2.csv")
```

###Continuing here from March!
```{r}
data.final <- read.csv("data.csv")

density_simple <- data.final %>%
  group_by(as.character(density_levels), density_category, density, microsite, phylum) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')
##Plot good for Appendix and Defence
ggplot(density_simple, aes(as.character(density_category), animals, color = microsite)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal density")

```

```{r}
ggplot(density_simple, aes(as.character(density_levels), animals)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal density")
```

```{r}
ggplot(density_simple, aes(as.character(density_levels), animals)) +
  geom_boxplot() +
  facet_wrap(~phylum) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal density")

```


```{r}
ggplot(density_simple, aes(as.character(density), richness)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") +
  labs(x = "shrub density", y = "total animal richness")
```
```{r}
data_simple <- data.final %>%
  group_by(as.character(density_levels), method, density_category, density, microsite) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')

ggplot(data_simple, aes(density_levels, animals, color = method)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") +
  theme_classic() + 
  labs(x = "shrub density level", y = "animal abundance")

```



```{r}
ggplot(data_simple, aes(density_levels, richness)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") +
  labs(x = "shrub density level", y = "animal richness")

```
##Cover Data
```{r}
density_simple2 <- data.final %>%
  group_by(as.character(density_levels), density_category, density, cover) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')

ggplot(density_simple2, aes(as.character(cover), animals)) +
  geom_bar(stat = "identity") +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal density") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
Does this work for cover?

###RDM Data
```{r}
density_simple3 <- data.final %>%
  group_by(as.character(density_levels), density_category, microsite, density) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')
```

```{r}
#RDM Set up
RDM <- read.csv("RDM.CSV")
data_RDM <- RDM %>%
  group_by(as.character(density_level), Site.Density, density, RDM_g, microsite) %>%
  summarise() %>%
  rename(density_level = 'as.character(density_level)')

names(data_RDM)[1] <- "density_levels"

```

#Merge RDM data with animal data!
```{r}
animal.RDM.data <- merge(density_simple3, data_RDM, all = TRUE)
```

```{r}
#RDM PLot (Use first for appendix?)
ggplot(animal.RDM.data, aes(RDM_g, animals, fill = microsite)) +
  geom_histogram(stat = "identity") +
  facet_wrap(~density_category) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "RDM (grams)", y = "animal density")
ggplot(animal.RDM.data, aes(RDM_g, animals, fill = microsite)) +
  geom_histogram(stat = "identity") +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "RDM (grams)", y = "animal density")
```

```{r}
#Diversity by shrub density by invert/vert
ggplot(density_simple, aes(as.character(density_levels), richness)) +
  geom_boxplot() +
  facet_wrap(~phylum) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal richness")
```

```{r}
#Climate Data
climate <- read_csv("Carrizo_micronet.csv")
data_climate <- climate %>%
  group_by(as.character(density_level), microsite, temp) %>%
  summarise() %>%
  rename(density_level = 'as.character(density_level)')
names(data_climate)[1] <- "density_levels"

density_simple4 <- data.final %>%
  group_by(as.character(density_levels), microsite) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')

animal.climate.data <- merge(data_climate, density_simple4, all = TRUE)
```

```{r}
#Compares Temperatures with animal abundances for each microsite (Use of Appendix?)
ggplot(animal.climate.data, aes(temp, animals, fill = density_levels)) +
  geom_histogram(stat = "identity") +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "Temperature", y = "animal density")
#Compares Temperatures with animal abundance
ggplot(animal.climate.data, aes(temp, animals, fill = microsite)) +
  geom_histogram(stat = "identity") +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "Temperature", y = "animal density")
#Compares Site Density temperatures
ggplot(animal.climate.data, aes(as.character(density_levels), temp)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal richness")
#Shows Compares site density temperature in both microsites
ggplot(animal.climate.data, aes(as.character(density_levels), temp)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  facet_wrap(~microsite)
  labs(x = "shrub density level", y = "temperature")
```
```{r}
density_simple5 <- data.final %>%
  group_by(as.character(density_levels), density, microsite, phylum) %>%
  summarise(animals = sum(daily_animal_totals), richness = n()) %>%
  rename(density_levels = 'as.character(density_levels)')

data_RDM2 <- RDM %>%
  group_by(as.character(density_level), density, microsite) %>%
  summarise(RDM = mean(RDM_g)) %>%
  rename(density_level = 'as.character(density_level)')
names(data_RDM2)[1] <- "density_levels"

data_climate2 <- climate %>%
  group_by(as.character(density_level), microsite) %>%
  summarise(mean_temp = mean(temp), max_temp = max(temp)) %>%
  rename(density_level = 'as.character(density_level)')
names(data_climate2)[1] <- "density_levels"

rdm.climate <- merge(data_climate2, data_RDM2, all = TRUE)
final.data <- merge(density_simple5, rdm.climate, all = TRUE)
```

###Final Stats
```{r}
#Animal Abundance by Density Level and Microsite
m1 <- glm(animals ~ density_category*microsite, family = "poisson", data = density_simple)
anova(m1, test = "Chisq")
e1 <- emmeans(m1, pairwise~density_category*microsite)
e1
```

```{r}
#Animal Abundance by Density Level
m2 <- glm(animals~density_levels, family = "poisson", data = density_simple)
anova(m2, test = "Chisq")
e2 <- emmeans(m2, pairwise~density_levels)
e2
```

```{r}
#Animal Abundance by Density level and Phylum
m3 <- glm(animals~density_levels*phylum, family = "poisson", data = density_simple)
anova(m3, test = "Chisq")
e3 <- emmeans(m3, pairwise~density_levels*phylum)
e3
```

```{r}
#Animal Richness by Density Level
m4 <- glm(richness~density, family = "quasipoisson", data = density_simple)
anova(m4, test = "Chisq")
emmeans(m4, pairwise~density)
```

```{r}
#Animal Abundance by Method and Density level
m5 <- glm(animals~method*density_levels, family = "poisson", data = data_simple)
anova(m5, test = "Chisq")
e5 <- emmeans(m5, pairwise~method*density_levels)
e5
```

```{r}
#Animal Abundance by Density Level
m6 <- glm(animals~density_levels, family = "poisson", data = data_simple)
anova(m6, test = "Chisq")
emmeans(m6, pairwise~density_levels)

```

```{r}
#Cover Stats
m7 <- glm(animals~density_category*cover, family = "poisson", data = density_simple2)
m7
anova(m7, test = "Chisq")
e7 <- emmeans(m7, pairwise~density_category*cover)
e7
```

```{r}
#RDM Stats
m8 <- glm(animals~density_category*RDM_g, family = "poisson", data = animal.RDM.data)
m8
anova(m8, test = "Chisq")
e8 <- emmeans(m8, pairwise~density_category*RDM_g)
e8

```
```{r}
#Animal Abundance by Density Level and Phylum
m17 <- glm(animals ~ density_category*phylum, family = "poisson", data = density_simple)
anova(m17, test = "Chisq")
e17 <- emmeans(m16, pairwise~density_category*phylum)
e17
```
```{r}
#Animals compared to temp and density level
m9 <- glm(animals ~ temp*density_levels, family = "poisson", data = animal.climate.data)
anova(m9, test = "Chisq")
e9 <- emmeans(m9, pairwise~temp*density_levels)
e9
#Significant Difference Between Low - Medium, Low - High and Medium - High Plots
```
```{r}
#Animals compared to temp and microsite
m10 <- glm(animals ~ temp*microsite, family = "poisson", data = animal.climate.data)
anova(m10, test = "Chisq")
e10 <- emmeans(m10, pairwise~temp*microsite)
e10
#Significant difference between Shrub and open animal interactions with temperature as a factor
```
```{r}
#Comparing Temp to density levels
m11 <- glm(temp ~ density_levels, family = "poisson", data = animal.climate.data)
anova(m11, test = "Chisq")
e11 <- emmeans(m11, pairwise~density_levels)
e11
#Significant difference between Medium - High Density Plots and Low - High Density Plats
```
```{r}
#Comparing Temp vetween Density levels and microsites
m12 <- glm(temp ~ density_levels*microsite, family = "poisson", data = animal.climate.data)
anova(m12, test = "Chisq")
e12 <- emmeans(m12, pairwise~density_levels*microsite)
e12
#Significant difference between Low open - High Shrub, Medium Open - High Shrub, Medium Shrub - High Shrub, Which supports why we see more animals at the medium plots
##Somethings Up with the numbers though. Looks weird when knitted
```

```{r}
#Stats for animal abundance with density level by micorsite with RDM and mean temp as covariates
m13 <- glm(animals ~ density_levels*microsite+RDM+mean_temp, family = "quasipoisson", data = final.data)
anova(m13, test = "Chisq")
e13 <- emmeans(m13, pairwise~density_levels*microsite)
e13
#emmeans seems to not yield any data for this
```

```{r}
#Stats for Animal Richness by density level with RDM and mean temp as covariates
m14 <- glm(richness ~ density_levels*microsite+RDM+mean_temp, family = "gaussian", data = final.data)
anova(m14, test = "Chisq")
e14 <- emmeans(m14, pairwise~density_levels*microsite)
e14
#Again emmeans seems to not work here
```
```{r}
##Stats for Animal Abundance by density level with RDM and max temp as covariates
m15 <- glm(animals ~ density_levels*microsite+RDM+max_temp, family = "quasipoisson", data = final.data)
anova(m15, test = "Chisq")
e15 <- emmeans(m15, pairwise~density_levels*microsite+RDM+max_temp)
e15
#again emmeans yields NA
```
```{r}
##Stats for Animal Richness by density level with RDM and max temp as covariates
m16 <- glm(richness ~ density_levels*microsite+RDM+max_temp, family = "gaussian", data = final.data)
anova(m16, test = "Chisq")
e16 <- emmeans(m16, pairwise~density_levels*microsite+RDM+max_temp)
e16
#Again emmeans yields NA
```



####Possible figures For Publication
```{r}
#Diversity by shrub density by invert/vert
ggplot(density_simple, aes(as.character(density_levels), richness)) +
  geom_boxplot() +
  facet_wrap(~phylum) +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal richness")
```
```{r}
#Comparison of animal density to individual shrub densities
ggplot(density_simple, aes(as.character(density), richness)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") +
  labs(x = "shrub density", y = "total animal richness")
```
```{r}
#Displays animal density to each established plot
ggplot(density_simple, aes(as.character(density_levels), animals)) +
  geom_boxplot() +
  scale_color_brewer(palette = "Set1") + theme_classic() +
  labs(x = "shrub density level", y = "animal density")
```

```{r}
pca <- prcomp(t(community), center = TRUE)
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1)
barplot(pca.var.per, main="Scree Plot", xlab="Principal Component", ylab="Percent Variation")
pca.data <- data.frame(Sample=rownames(pca$x),
  X=pca$x[,1],
  Y=pca$x[,2])
pca.data
ggplot(data=pca.data, aes(x=X, y=Y, label=Sample)) +
  geom_text() +
  xlab(paste("PC1 - ", pca.var.per[1], "%", sep="")) +
  ylab(paste("PC2 - ", pca.var.per[2], "%", sep="")) +
  theme_bw() +
  ggtitle("My PCA Graph")
distance.matrix <- dist(scale(t(community), center=TRUE, scale=TRUE),
  method="euclidean")
mds.stuff <- cmdscale(distance.matrix, eig=TRUE, x.ret=TRUE)
mds.var.per <- round(mds.stuff$eig/sum(mds.stuff$eig)*100, 1)
mds.var.per
mds.values <- mds.stuff$points
mds.data <- data.frame(Sample=rownames(mds.values),
  X=mds.values[,1],
  Y=mds.values[,2])
mds.data
ggplot(data=mds.data, aes(x=X, y=Y, label=Sample)) +
  geom_text() +
  theme_bw() +
  xlab(paste("MDS1 - ", mds.var.per[1], "%", sep="")) +
  ylab(paste("MDS2 - ", mds.var.per[2], "%", sep="")) +
  ggtitle("MDS plot using Euclidean distance")
log2.community <- log2(community)
log2.community <- matrix(0,
  nrow=ncol(log2.community),
  ncol=ncol(log2.community),
  dimnames=list(colnames(log2.community),
    colnames(log2.community)))
log2.community
for(i in 1:ncol(log2.community)) {
  for(j in 1:i) {
    log2.community[i, j] <-
      mean(abs(log2.community[,i] - log2.community[,j]))
  }
}
log2.community

mds.stuff <- cmdscale(as.dist(log2.community),
  eig=TRUE,
  x.ret=TRUE)
mds.var.per <- round(mds.stuff$eig/sum(mds.stuff$eig)*100, 1)
mds.var.per
mds.values <- mds.stuff$points
mds.data <- data.frame(Sample=rownames(mds.values),
  X=mds.values[,1],
  Y=mds.values[,2])
mds.data
 
ggplot(data=mds.data, aes(x=X, y=Y, label=Sample)) +
  geom_text() +
  theme_bw() +
  xlab(paste("MDS1 - ", mds.var.per[1], "%", sep="")) +
  ylab(paste("MDS2 - ", mds.var.per[2], "%", sep="")) +
  ggtitle("MDS plot using avg(logFC) as the distance")
```